Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed renaming of the parametrization and validation entries

```{r echo=FALSE}
#Cross tally the model structure with parametrization and validation categories
#FIXME: Check that studies are either not being under counted or double-counted. What do I want to count here? Is it the unique studies per method or combined method because most studies used a combination of parametrization methods especially
parametrization_and_validation_by_model_structure <- data_without_fmd %>%
  mutate(parametrization = str_replace(parametrization, ' ', ' + '),
         validation = str_replace(validation, ' ', ' + ')
         ) %>% 
  count(model_structure, parametrization, validation) %>% 
  pivot_wider(names_from = model_structure, values_from = n)

@@

```{r echo=FALSE}
#Keep only the unique entries
parametrization_and_validation_count <- data_without_fmd %>% 
  mutate(parametrization = str_replace(parametrization, ' ', ' + '), 
         validation = str_replace(validation, ' ', ' + ')
         ) %>% 
  count(parametrization, 
        validation, 
        name = 'num_of_studies'
        ) %>% 
  group_by(parametrization) %>% 
  arrange(desc(num_of_studies), .by_group = T)

>>>>

```{r echo=FALSE}
#Cross tally the model structure with parametrization and validation categories
#FIXME: Check that studies are either not being under counted or double-counted. What do I want to count here? Is it the unique studies per method or combined method because most studies used a combination of parametrization methods especially
parametrization_and_validation_by_model_structure <- data_without_fmd %>%
  count(model_structure, parametrization, validation) %>% 
  pivot_wider(names_from = model_structure, values_from = n)

@@

```{r echo=FALSE}
#Keep only the unique entries
parametrization_and_validation_count <- data_without_fmd %>% 
  count(parametrization, 
        validation, 
        name = 'num_of_studies'
        ) %>% 
  group_by(parametrization) %>% 
  arrange(desc(num_of_studies), .by_group = T)
